% =============================================================================
% related_work_section.tex --- Positional Distillation Paper
% Self-contained related work section (~1.5 pages)
% Usage: \input{related_work_section.tex} in main.tex
% =============================================================================

\section{Related Work}
\label{sec:related_work}

\paragraph{Knowledge Distillation for Language Models.}
Knowledge distillation~\citep{hinton2015distilling} transfers knowledge from a teacher to a smaller student via soft targets.
\citet{kim2016sequence} extended this to sequence models with word-level and sequence-level objectives.
For autoregressive LLMs, the choice of divergence and data distribution is decisive.
\citet{gu2024minillm} argued for reverse KL in generative LLM distillation, on the grounds that reverse KL avoids the student placing probability on low-support teacher regions; \citet{agarwal2024onpolicy} introduced Generalized Knowledge Distillation (GKD), which generates rollouts from the student (``on-policy'') and supervises with teacher logits---substantially outperforming supervised off-policy distillation on reasoning tasks.
\citet{ko2024distillm} proposed skew KL and an adaptive off-policy schedule; \citet{wen2023fdivergence} generalized sequence-level KD to arbitrary $f$-divergences; \citet{wu2025rethinking} revisited the mode- vs.\ mean-seeking interpretation of reverse and forward KL in the LLM setting and showed that both converge under sufficient training but differ in which distribution regions they first concentrate on.
\citet{xu2025speculative} introduced Speculative Knowledge Distillation, which interleaves teacher-student sampling in the style of speculative decoding and filters tokens the teacher would not have produced.
Our work builds directly on the on-policy reverse-KL paradigm of \citet{gu2024minillm} and \citet{agarwal2024onpolicy}, but asks a different question: holding the divergence and data distribution fixed, \emph{which token positions along the student's rollout carry useful signal?} Our answer---only the early window (Early Stopping Rollout)---is orthogonal to the divergence-design axis these works explore.

\paragraph{Token-Level Importance in Distillation and Reasoning.}
A growing body of work demonstrates that not all tokens contribute equally to learning.
\citet{wang2025beyond8020} showed that only $\sim$20\% of chain-of-thought tokens have high entropy, and these ``forking tokens'' steer reasoning paths---applying RL gradients to only these tokens matches full-gradient performance.
In the RL fine-tuning setting, \citet{vassoyan2025ignorekl} demonstrated that uniform KL penalties across all token positions prevent exploration on ``critical tokens'' where the pretrained model is most uncertain, and proposed entropy-weighted KL relaxation that allows the model to deviate from its prior precisely where it needs to learn.
\citet{li2025preplan} discovered a ``preplan-and-anchor'' mechanism in LLM attention patterns, where models first perform long-range contextual reference before producing semantic anchor tokens, enabling targeted credit assignment.
\citet{singh2026functional} proposed greedy pruning of reasoning chains and showed that LLMs internally encode token-level functional importance for answer generation.

In the distillation setting specifically, several concurrent works have explored token selection.
\citet{huang2025selectkd} proposed SelecTKD, a propose-and-verify framework where the teacher verifies student-proposed tokens, applying full loss to accepted tokens and masking rejected ones.
\citet{xie2026adakd} introduced AdaKD, which adaptively adjusts token-level temperature based on learning stability.
\citet{tavor2026rethinking} systematically disentangled selective KD along position, class, and sample axes, proposing student-entropy-guided position selection (SE-KD) that reduces wall time by 70\% without sacrificing accuracy.
\citet{kim2026tsdkd} combined entropy-based token selection with preference ranking in a dual distillation framework.

These works collectively establish that not all tokens deserve equal gradient weight, and most of them pick the ``important'' tokens via a scalar per-token criterion---entropy, KL, difficulty, or a verification score.
Our Section~\ref{sec:token_selection} ablation directly contradicts the premise that such scalars are sufficient: selecting the same number of tokens by top-KL, top-entropy (student, teacher, AND, OR, triple-product), soft-weighted joint entropy, or top-$K$-renorm RKL (a vocabulary-level renormalization of RKL proposed for stabilizing distillation; exact citation to be added in camera-ready)%
\footnote{TODO: resolve and cite the top-$K$-renorm RKL method (Fu et al., 2025).}
all underperform \method{} and most underperform plain full-sequence training.
Position is the load-bearing axis; scalar token saliencies are not.
This also resolves a tension with \citet{wang2025beyond8020}, who find that RL gradients concentrated on high-entropy ``forking tokens'' suffice: in on-policy \emph{distillation}, the high-entropy tokens are disproportionately in the uncontaminated early window, so their result is consistent with ours once this early-window concentration of entropy is accounted for.

% \paragraph{Training Stability and Sequence-Level Issues.}
% Full-sequence on-policy distillation is known to suffer from instability.
% \citet{holtzman2020curious} identified that likelihood-based training can produce bland, repetitive text---a form of neural text degeneration.
% \citet{shumailov2024collapse} demonstrated that iteratively training generative models on their own outputs leads to model collapse, where distribution tails disappear.
% In on-policy KD specifically, \citet{jang2026veto} proposed Veto, a geometric bridge in logit space that suppresses harmful gradients on low-confidence tokens, directly addressing the instability we also observe.
% Our approach is complementary: rather than modifying the target distribution, we restrict the loss scope to early positions where teacher-student agreement is naturally highest, achieving stability through a simpler mechanism.

% Several works have studied how sequence length affects distillation quality.
% \citet{chen2025distillingessence} showed that training on only the first 50\% of tokens in supervised reasoning distillation retains $\sim$91\% of full-sequence performance, establishing a computation-quality tradeoff.
% \citet{yan2026dasd} addressed exposure bias and capacity misalignment in long chain-of-thought distillation through temperature-scheduled learning.
% Our work extends the truncation insight to the on-policy setting: we demonstrate that positional loss masking on student-generated sequences achieves equal or better performance than full-sequence loss, while providing the additional benefit of eliminating degenerate repetition patterns that are unique to on-policy training.

% \paragraph{Curriculum Learning and Sequence Scheduling.}
% Curriculum learning~\citep{bengio2009curriculum} improves training by gradually increasing task difficulty.
% \citet{bengio2015scheduled} applied this principle to sequence models through scheduled sampling, transitioning from teacher-forced to free-running generation during training.
% In the LLM pretraining setting, \citet{li2022stability} showed that long sequences at training start cause extreme gradient variance, and sequence length warmup stabilizes training while enabling larger batch sizes.
% \citet{pouransari2024dataset} extended this with variable sequence length curriculum for LLM pretraining, achieving up to 3$\times$ faster convergence.
% Our progressive position schedule---linearly increasing the position limit from 1 to 200 over training---applies the curriculum principle to the distillation loss scope rather than to the input sequence length, and represents a novel form of curriculum specific to knowledge distillation.

% \paragraph{Reasoning Distillation.}
% Chain-of-thought prompting~\citep{wei2022chainofthought} made intermediate reasoning the unit of transfer for distillation, and the DeepSeek-R1 release~\citep{deepseekr1} established that SFT-distilling a strong reasoner into a smaller model is often competitive with direct RL on the small model.
% Our experiments include three reasoning tasks (MATH-500, HumanEval/MBPP, BFCL) and a 1.5B-math-student $\to$ 8B-teacher sweep; \method{} surpasses the teacher on several of these cells (Qwen math, function-calling), indicating that reasoning-distillation gains beyond the teacher are possible when the mode-seeking reverse-KL loss is restricted to the planning region.
% This is a complementary perspective to the DeepSeek-R1 recipe, which uses fully-sequenced SFT: our analysis explains why the on-policy, early-stopped-rollout regime is both more efficient and more stable for reasoning-style chain-of-thought distillation, and why full-sequence on-policy distillation---which in principle should be the strongest setting---frequently degrades across training on coding and math.
